---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ROCsurf

<!-- badges: start -->
[![codecov](https://codecov.io/gh/ErtanSU/ROCsurf/graph/badge.svg?token=H5HIYVDUZU)](https://codecov.io/gh/ErtanSU/ROCsurf)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ROCsurf)](https://cran.r-project.org/package=ROCsurf)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![R-CMD-check](https://github.com/ErtanSU/ROCsurf/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ErtanSU/ROCsurf/blob/master/.github/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The objective of this project is to assess the Receiver Operating Characteristic
(ROC) surfaces for Gamma, Weibull, and Logistic distributions. Additionally, it 
supports performance evaluations linked to these ROC surfaces in the context of 
three-class problems.

## Installation

You can install the development version of ROCsurf via the following code:
  
  ``` r
# install.packages("devtools")
devtools::install_github("ErtanSU/ROCsurf")
```

## Example

This is a basic example which shows you how to solve a common problem:
  
```{r}
library(ROCsurf)
dG(c(1,2,3,4,5,200,1000),alpha=6,beta=.8)
dW(c(1,2,3,4,5,200,10000),alpha=1,beta=2)
dL(c(1,2,3,4,5,200),alpha=1,beta=.1)
```

```{r}
library(ROCsurf)
pG(c(.5,1,2,3,4,25),alpha=6,beta=.8)
pW(c(.5,1,2,3,4,100),alpha=1,beta=2)
pL(c(.5,1,2,100),alpha=1,beta=.1)
```

```{r}
library(ROCsurf)
qG(c(.9971,0.5,0.3),alpha=6,beta=.8)
qW(c(.9971,0.5,0.3),alpha=1,beta=2)
qL(c(.9971,0.5,0.3),alpha=1,beta=.1)
```

```{r}
library(ROCsurf)
rG(10,alpha=6,beta=.8)
rW(10,alpha=1,beta=2)
rL(10,alpha=1,beta=.1)
```

```{r}
library(ROCsurf)
x<-rW(100,  2,  1)
y <- rG(100,  2, 2)
z <- rW(100,  6,  9)
r.tc_vus(x=x,y=y,z=z,
         init_param=c(alpha1=2,beta1=1,alpha2=2,beta2=2,
                      alpha3=6,beta3=9),
         model=c("WGW"), method=c("MLE"))
```

```{r}
library(ROCsurf)
x<- rW(100,  2,  1)
y <- rG(100,  2, 2)
z <- rW(100,  6,  9)
r.tc_index(x=x,y=y,z=z,
           init_param=c(alpha1=2,beta1=1,alpha2=2,
                        beta2=2,alpha3=6,beta3=9),
           init_index=c(median(x),median(y)),
           model=c("WGW"),
           method=c("MLE"))
```


